Co-citations in context

### 2019-09-12 cocit_r_v2.tex
Revert "small fixes to response to review"
This reverts commit 7daf4f076b8cc61436aff618ea79e6566058aa92.

\begin{itemize}
\item An illustration has been generated that will become part of supplementary material.
\item Yes, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around. The local model accounts for this but the global one does not. We argue consistently that local models reduce mis-specification.
\item The relationship between novelty/conventionality and citation impact is not a ground truth, we have never claimed it is. This framework was developed by Uzzi et al. (2013) and we have used it to enable \emph{ceteris paribus} comparisons. We cannot address the question of the huge unstated assumption- we don't think we make such an assumption.
\end{itemize}

@@

\textcolor{blue}{A related study by \cite{wang_bias_2017} also uses journal pairings to study novelty in scientific publications, but focuses on previously undetected journal pairs to generate a novelty index. }

>>>>

\begin{itemize}
\item An illustration has been generated that will become part of supplementary material.
\item Yes, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around. The local model accounts for this but the global one does not. We argue consistently that local models reduce mis-specification.
\item The relationship between novelty and conventionality is not a ground truth, we have never claimed it is. This framework was developed by Uzzi et al. (2013) and we have used it to enable \emph{ceteris paribus} comparisons. We cannot address the question of the huge unstated assumption- we don't think we make such an assumption.
\end{itemize}

@@

\textcolor{blue}{A related study by \cite{wang_bias_2017} also uses journal pairings to study novelty in scientific publications but focuses on previously undetected journal pairs to generate a novelty index}
